---
title: "PA1_template.Rmd"
author: "Stephan Regenass"
date: "20 Mar 2016"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 1 (R Markdown) 

This is an literate programming (R Markdown) document which documents my solution to **assignment 1** of Coursera Course Reproducible Research.

###Loading and Preprocessing the data: ###

1. Load the data:

```{r read.data}
activity<-read.csv("activity.csv")
# summary(activity)
```

2. Preprocess the data: 
Convert **date** to Date class and **interval** to Factor class

```{r convert date}
activity$date <- as.Date(activity$date, format = "%Y-%m-%d")
activity$interval <- as.factor(activity$interval)
str(activity)
```

###What is (mean?) total number of steps taken per day?###
*comment: the assignment mentions "mean" - is this a typo?*

1. Calculate the total number of steps per day:

```{r calculateStepsAday}
stepsAday<-aggregate(steps ~ date, activity, sum)
print(stepsAday)
```

2. Make a histogram of the total number of steps taken each day:

```{r makeHistogram}
hist(stepsAday$steps, main="total number of steps taken each day",xlab="number of steps per day")
```

3. Calculate the mean and median of the total steps taken per day:

```{r MeanMedian}
stepsMean<-mean(stepsAday$steps)
stepsMedian<-median(stepsAday$steps)
```

Per day the mean number of steps is `r format(stepsMean, nsmall=3)` and the median is `r stepsMedian` .

###What is the average daily activity pattern?###

1. Make a time series plot  of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r timePlot}
#plot(activity$interval,activity$steps,type="l")
```

2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r maxStepInterval}
#which.max(activity$steps)
```